Incremental Construction of Programs in a Multitask Setting

### 2013-10-23 drafts/nips/nips2013.tex

>>>>

\section{Application to Graphical Model Structure Learning}

Learning the structure of graphical models that capture the independencies underlying a dataset is an active area of research\cite{adams-wallach-ghahramani-2010a}\cite{ISI:000240797500002}\cite{ISI:000178037200004}\cite{ISI:A1995RX35400001}. Graphical model structures enforce the conditional independences a modeler believes exists among latent and observed random variables\cite{DBLP:books/daglib/0066829}.
